The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-22 formalwriteup.tex
Line edits

Recall by Lemma~\ref{lem:dFdxi} that $\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$. In terms of $G(z)$, we can calculate $\partial_{y_2-y_1}(F_1(z))$ as
\begin{align*}
\partial_{y_2-y_1}(F_1(z))
&=-\frac{z}{(1-x_1z)^2}F(z)+\frac{1}{1-x_1z}\partial_{y_2-y_1}(F(z))\\
&=-\frac{z}{1-x_1z}F_1(z)+\frac{1}{1-x_1z}\left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_2z}\right)F(z)+\frac{G(z)}{1-x_1z}\\
&=\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{G(z)}{1-x_1z}.
\end{align*}
In addition, we have that 
\[
\frac{1-s_{1i}}{x_1-x_i}(F_1(z))
=\frac{1}{x_1-x_i}\left(\frac{1}{1-x_1z}-\frac{1}{1-x_iz}\right)F(z)=\frac{z}{(1-x_iz)(1-x_1z)}F(z)=\frac{z}{1-x_iz}F_1(z).
\]
Because $F_1(z)$ is invariant under $s_{ij}$ for $i,j > 1$, we now compute
\begin{align*}
D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)F_1(z)\\
&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}F_1(z)+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
&=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z).
\end{align*}
To show that the $z^p$ coefficient in $D_{y_2-y_1}(F_1(z))$ vanishes, we must consider $\frac{\partial F_1}{\partial z}$.  By Lemma~\ref{lem:dFdz}, we have
\[
\frac{\partial F}{\partial z}=V(z) - \sum_j \frac{cx_j}{1-x_jz}F(z),
\]
where $[z^l]V(z)=0$ for $l=0,\dots,p-1$. From this, it follows that
\begin{align*}
\frac{\partial F_1}{\partial z} = \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_1z}\right) &=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
&=\frac{V(z)}{1-x_1z}-\frac{1}{1-x_1z}\sum_j \frac{cx_j}{1-x_jz}F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
&=\frac{V(z)}{1-x_1z} - \sum_j \frac{cx_j}{1-x_jz}F_1(z)+\frac{x_1}{1-x_1z} F_1(z).
\end{align*}
We now compute
\begin{align*}
D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z) + \sum_{j} \left(\frac{zc}{1-x_jz} - zc\right) F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)-\frac{x_1z^2}{1-x_1z}F_1(z)+\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
&=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z},
\end{align*}
where in the second step we have subtracted $n zc F_1(z)$.  We note that $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$, hence a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$. By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi}, these coefficients of $G(z)$ and $V(z)$ are all $0$, hence $[z^p]\left(\frac{G(z)+z^2V(z)}{1-x_1z}\right)=0$. We conclude that 
\[
[z^p]D_{y_2-y_1}(F_1(z))=[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right).
\]
If $b=[z^{p-1}](F_1(z))$, then $[z^p](-zF_1(z))=-b$ and $[z^p]\left(-z^2\frac{\partial F_1}{\partial z}\right)=b$, which implies that 
\[
D_{y_2 - y_1} f_1 = [z^p]D_{y_2-y_1}(F_1(z))= [z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right) = -b + b = 0. \qedhere
\]
\end{proof}

@@

Consider the ideal
\[
I = \langle f_1, \ldots, f_{n - 1} \rangle \subset A
\]
generated by the $f_i$.  In this section, we will show that $A/I$ is a complete intersection, for which we require some preparatory computations.

@@

\begin{lemma}\label{lem:vand}Let $s_1, \ldots, s_{r }$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ are linearly independent.
\end{lemma}
\begin{proof} 
Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.  Then $\left(\prod_j (1-s_jz)\right)\left(\sum_i \frac{\lambda_i}{1-s_iz}\right)$ must be $0$ in the ring of formal power series. Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-s_iz}=0$. In particular for $l=0,\dots,r-1$ we have $\sum_i \lambda_is_i^l=0$.  However, the vectors $(1,s_i,\dots,s_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
\end{proof}

@@

\begin{lemma} \label{lem:resbyparts}
Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.  For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
\end{lemma}
\begin{proof} 
We will use an analogue of ``residues by parts'' in a formal power series setting.   We first show that 
\[
a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z)
\]
for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)$. We now compute
\begin{align*}
a'(z)&=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)\\
&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}+\sum_j \frac{-cm_js_j}{1-s_jz}a(z)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
\end{align*}
The fact that $[z^l]V(z)=0$ for $0 \le l \le p-1$ then gives the claim.

Now, for any integer $l$, define the Laurent polynomial 
\[
h_l(z)=z^{-l-r}\prod_i(1-s_iz).
\]
Notice that
\begin{align*}
\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) + h_l(z) a'(z) \\
&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_im_i c}{1 - s_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
&= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
\end{align*}
We note that 
\[
-\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z)
\]
is a Laurent polynomial with lowest degree term 
\[
- z^{-l-r-1} \left(l + r + \sum_i s_i m_i c\right) = - z^{-l-r-1}(l+ r)
\]
and highest degree term 
\[
- z^{-l - 1} (-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right).
\]
The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$. We always have 
\[
[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0,
\]
so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$, which is nonzero for $c$ generic and $\prod_i s_i \ne 0$. Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
\end{proof}

@@

\begin{proposition}\label{prop:ci}
For generic $c$, the quotient $A/I$ is a complete intersection. 
\end{proposition}
\begin{proof}
It suffices to show that if $x_1,\dots,x_{n} \in k$ satisfy $f_i(x_1,\dots,x_{n})=0$ for all $i$, then $x_1=\dots=x_{n}=0$.  Suppose that the $x_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.  In these terms, we have that 
\[
[z^p]\left(\frac{1}{1-s_iz}F(z)\right)= 0
\]
for $i = 1, \ldots, r $ and wish to show that $r=1$ and $s_1=0$.

We first claim that at least one $s_i$ is $0$. Suppose for the sake of contradiction that $\prod_i s_i \ne 0$.  We recall
\[
a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
\]
as in Lemma~\ref{lem:resbyparts}.  Recall that $b_i(z)=\prod_{j \ne i} (1-s_jz)$ for $i=1,\dots,r$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-s_iz}F(z)$ so in particular 
\[
[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-s_iz}F(z)=0.
\]
Therefore for any $\lambda_i \in k$, we have
\begin{equation}\label{eq:lincomb}
\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p]\left( a(z)\sum_{i=1}^{r}\lambda_ib_i(z)\right)=0.
\end{equation}
By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$. Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that $\sum_i\lambda_i^mb_i(z)=z^m$. Choosing these $\lambda_i^m$ in (\ref{eq:lincomb}), we see that
\[
[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0.
\]
By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$, we find that 
\[
[z^l]a(z)=0 \text{ for $l=p-r,p-r-1,\dots,0$}.
\]
This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $s_i=0$ for some $i$.

>>>>

Recall by Lemma~\ref{lem:dFdxi} that $\partial_{y_2-y_1}(F(z))= G(z) - \left(\frac{zc}{1-x_2z}-\frac{zc}{1-x_1z}\right)F(z)$ for a power series $G(z)$ with $[z^l]G(z)=0$ for $l=0,\dots,p$. In terms of $G(z)$, we can calculate $\partial_{y_2-y_1}(F_1(z))$ as
\begin{align*}
\partial_{y_2-y_1}(F_1(z))
&=-\frac{z}{(1-x_1z)^2}F(z)+\frac{1}{1-x_1z}\partial_{y_2-y_1}(F(z))\\
&=-\frac{z}{1-x_1z}F_1(z)+\frac{1}{1-x_1z}\left(\frac{zc}{1-x_1z}-\frac{zc}{1-x_2z}\right)F(z)+\frac{G(z)}{1-x_1z}\\
&=\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{G(z)}{1-x_1z}.
\end{align*}
In addition, we have that 
\[
\frac{1-s_{1i}}{x_1-x_i}(F_1(z))
=\frac{1}{x_1-x_i}\left(\frac{1}{1-x_1z}-\frac{1}{1-x_iz}\right)F(z)=\frac{z}{(1-x_iz)(1-x_1z)}F(z)=\frac{z}{1-x_iz}F_1(z).
\]
Because $F_1(z)$ is invariant under $s_{ij}$ for $i,j > 1$, we now compute
\begin{align*}
D_{y_2-y_1}(F_1(z))&=\left(\partial_{y_2-y_1}-c\frac{1-s_{12}}{x_2-x_1}+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}\right)F_1(z)\\
&=\partial_{y_2-y_1}(F_1(z))-c\frac{1-s_{12}}{x_2-x_1}F_1(z)+c\sum_{j > 1} \frac{1-s_{1j}}{x_1-x_j}F_1(z)\\
&=\frac{G(z)}{1-x_1z}+\left(\frac{z(c-1)}{1-x_1z}-\frac{zc}{1-x_2z}\right)F_1(z)+\frac{zc}{1-x_2z}F_1(z)+\sum_{j > 1} \frac{zc}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z).
\end{align*}
To show that the $z^p$ coefficient in $D_{y_2-y_1}(F_1(z))$ vanishes, we must consider $\frac{\partial F_1}{\partial z}$.  By Lemma~\ref{lem:dFdz}, we have
\[
\frac{\partial F}{\partial z}=V(z) - \sum_j \frac{cx_j}{1-x_jz}F(z),
\]
where $[z^l]V(z)=0$ for $l=0,\dots,p-1$. From this, it follows that
\begin{align*}
\frac{\partial F_1}{\partial z} = \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_1z}\right) &=\frac{1}{1-x_1z} \frac{\partial F}{\partial z}+\frac{x_1}{(1-x_1z)^2} F(z)\\
&=\frac{V(z)}{1-x_1z}-\frac{1}{1-x_1z}\sum_j \frac{cx_j}{1-x_jz}F(z)+\frac{x_1}{(1-x_1z)^2} F(z)\\
&=\frac{V(z)}{1-x_1z} - \sum_j \frac{cx_j}{1-x_jz}F_1(z)+\frac{x_1}{1-x_1z} F_1(z).
\end{align*}
We now compute
\begin{align*}
D_{y_2-y_1}(F_1(z))&=\frac{G(z)}{1-x_1z}-\frac{z}{1-x_1z}F_1(z)+\sum_{j} \frac{zc}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)+zF_1(z)-\frac{z}{1-x_1z}F_1(z) + \sum_{j} \left(\frac{zc}{1-x_jz} - zc\right) F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)-\frac{x_1z^2}{1-x_1z}F_1(z)+\sum_{j} \frac{x_jcz^2}{1-x_jz}F_1(z)\\
&=\frac{G(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z}+z^2\frac{V(z)}{1-x_1z}\\
&=\frac{G(z)+z^2V(z)}{1-x_1z}-zF_1(z)-z^2\frac{\partial F_1}{\partial z},
\end{align*}
where in the second step we have subtracted $n zc F_1(z)$.  We note that $[z^p]\,\frac{G(z)+z^2V(z)}{1-x_1z}$ is a linear combination of $[z^l](G(z)+z^2V(z))$ for $0 \le l \le p$, hence a linear combination of $[z^l]G(z)$ for $0 \le l \le p$ and $[z^l]V(z)$ for $0 \le l \le p-2$. By Lemmas~\ref{lem:dFdz} and \ref{lem:dFdxi}, these coefficients of $G(z)$ and $V(z)$ are all $0$, hence $[z^p]\,\frac{G(z)+z^2V(z)}{1-x_1z}=0$. We conclude that 
\[
[z^p]D_{y_2-y_1}(F_1(z))=[z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right).
\]
If $b=[z^{p-1}](F_1(z))$, then $[z^p](-zF_1(z))=-b$ and $[z^p]\left(-z^2\frac{\partial F_1}{\partial z}\right)=b$, which implies that 
\[
D_{y_2 - y_1} f_1 = [z^p]D_{y_2-y_1}(F_1(z))= [z^p]\left(-zF_1(z)-z^2\frac{\partial F_1}{\partial z}\right) = -b + b = 0. \qedhere
\]
\end{proof}

@@

Consider the ideal $I = \langle f_1, \ldots, f_{n - 1} \rangle \subset A$ generated by the $f_i$.  In this section, we will show that $A/I$ is a complete intersection, for which we require some preparatory computations.

@@

\begin{lemma}\label{lem:vand}Let $s_1, \ldots, s_{r }$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - s_j z)$ are linearly independent.
\end{lemma}
\begin{proof} 
Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.  Then $\prod_j (1-s_jz)\sum_i \frac{\lambda_i}{1-s_iz}$ must be $0$ in the ring of formal power series. Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-s_iz}=0$. In particular for $l=0,\dots,r-1$ we have $\sum_i \lambda_is_i^l=0$.  However, the vectors $(1,s_i,\dots,s_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
\end{proof}

@@

\begin{lemma} \label{lem:resbyparts}
Let $s_1,\dots,s_{r}$ be distinct non-zero elements of $k$ and $m_i$ positive integers so that that $\sum_i m_is_i=0$.  For any integer $l \le p-r$, $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\ldots$, $[z^{l+r}]a(z)$.
\end{lemma}
\begin{proof} 
We will use an analogue of ``residues by parts'' in a formal power series setting.   We first show that 
\[
a'(z)=z^pb(z)-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z)
\]
for some formal power series $b(z)$. By Corollary~\ref{corr:dFdz2} we have for some $V(z)$ where $[z^l]V(z)=0$ for $0 \le l \le p-1$ that $F'(z)=V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)$. We now compute
\begin{align*}
a'(z)=\frac{d}{dz}\left(\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)\right)&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F'(z)+\sum_{j=1}^{r}\frac{s_j}{(1-s_jz)\prod_{i=1}^{r}(1-s_iz)}F(z)\\
&=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}\left(V(z)+\sum_j \frac{-cm_js_j}{1-s_jz}F(z)\right)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
%&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}+\sum_j \frac{-cm_js_j}{1-s_jz}a(z)+\sum_{j=1}^{r}\frac{s_j}{1-s_jz}a(z)\\
&=\frac{V(z)}{\prod_{i=1}^{r}(1-s_iz)}-\sum_j \frac{(m_jc-1)s_j}{1-s_jz}a(z).
\end{align*}
The fact that $[z^l]V(z)=0$ for $0 \le l \le p-1$ then gives the claim.

Now, for any integer $l$, define the Laurent polynomial $h_l(z)=z^{-l-r}\prod_i(1-s_iz)$. Notice that
\begin{align*}
\frac{d}{dz}( h_l(z) a(z)) &= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) + h_l(z) a'(z) \\
&=  -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_i}{1 - s_iz} h_l(z) a(z) - h_l(z) \sum_j \frac{(m_j c - 1)s_i}{1 - s_ijz} a(z)  + z^ph_l(z) b(z)\\
%&= -(l + r)z^{-1} h_l(z) a(z) - \sum_i \frac{s_im_i c}{1 - s_iz} h_l(z) a(z) + z^ph_l(z) b(z)\\
&= -\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z) a(z) + z^ph_l(z) b(z).
\end{align*}
We note that 
\[
-\left((l + r) z^{-1} + \sum_i \frac{s_im_i c}{1 - s_iz}\right) h_l(z)
\]
is a Laurent polynomial with lowest degree term 
\[
- z^{-l-r-1} \left(l + r + \sum_i s_i m_i c\right) = - z^{-l-r-1}(l+ r)
\]
and highest degree term 
\[
- z^{-l - 1} (-1)^r  \prod_i s_i\left((l + r) - \sum_i m_i c\right).
\]
The lowest degree term of the formal power series $z^ph_l(z)b(z)$ has degree at least $p-l-r$. We always have 
\[
[z^{-1}]\,\frac{d}{dz}( h_l(z) a(z))=0,
\]
so for $p-l-r \ge 0$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_l(z) a(z))\right)=0$ is a linear combination of $[z^l]a(z)$, $\ldots$, $[z^{l+r}]a(z)$ in which $[z^l]a(z)$ has coefficient $(-1)^r \prod_i s_i\left((l + r) - \sum_i m_i c\right)$, which is nonzero for $c$ generic and $\prod_i s_i \ne 0$. Therefore $[z^l]a(z)$ is a linear combination of $[z^{l+1}]a(z)$, $\dots$, $[z^{l+r}]a(z)$ when $l \le p-r$. 
\end{proof}

@@

\begin{proposition}\label{prop:ci}
For generic $c$, the quotient $A/I$ is a complete intersection. 
\end{proposition}
\begin{proof}
It suffices to show that if $x_1,\dots,x_{n} \in k$ satisfy $f_i(x_1,\dots,x_{n})=0$ for all $i$, then $x_1=\dots=x_{n}=0$.  Suppose that the $x_i$ take the distinct values $\{s_1,\dots,s_{r}\}$, where $s_i$ occurs with multiplicity $m_i>0$ so that $g(z)=\prod_i (1-s_iz)^{m_i}$.  In these terms, we have that 
\[
[z^p]\frac{1}{1-s_iz}F(z)= 0
\]
for $i = 1, \ldots, r $ and wish to show that $r=1$ and $s_1=0$.

We first claim that at least one $s_i$ is $0$. Suppose for the sake of contradiction that $\prod_i s_i \ne 0$.  We recall
\[
a(z)=\frac{1}{\prod_{i=1}^{r}(1-s_iz)}F(z)
\]
as in Lemma~\ref{lem:resbyparts}.  Recall that $b_i(z)=\prod_{j \ne i} (1-s_jz)$ for $i=1,\dots,r$.   Now, for any $i$, we have $a(z)b_i(z)=\frac{1}{1-s_iz}F(z)$ so in particular 
\[
[z^p]a(z)b_i(z)=[z^p]\frac{1}{1-s_iz}F(z)=0.
\]
Therefore for any $\lambda_i \in k$, we have
\begin{equation}\label{eq:lincomb}
\sum_{i=1}^{r} \lambda_i[z^p]a(z)b_i(z)=[z^p] \,a(z)\sum_{i=1}^{r}\lambda_ib_i(z)=0.
\end{equation}
By Lemma~\ref{lem:vand}, $b_i(z)$ are linearly independent polynomials of degree at most $r-1$. Therefore for $0 \le m \le r-1$ we can choose $\{\lambda_i^m\}$ so that $\sum_i\lambda_i^mb_i(z)=z^m$. Choosing these $\lambda_i^m$ in (\ref{eq:lincomb}), we see that
\[
[z^{p-r+1}]a(z)=\dots=[z^p]a(z)=0.
\]
By repeated application of Lemma~\ref{lem:resbyparts} starting with $l=p-r$, we find that 
\[
[z^l]a(z)=0 \text{ for $l=p-r,p-r-1,\dots,0$}.
\]
This implies that $[z^0]a(z)=0$, a contradiction. We conclude that $s_i=0$ for some $i$.
